CUTIE: Learning to Understand Documents with Convolutional Universal Text Information Extractor

### 2019-06-20 Article/ms.tex
final

%%%%%%%%% ABSTRACT
\begin{abstract}
   Extracting key information from documents, such as receipts or invoices, and preserving the interested texts to structured data is crucial in the document-intensive streamline processes of office automation in areas that includes but not limited to accounting, financial, and taxation areas. To avoid designing expert rules for each specific type of document, some published works attempt to tackle the problem by learning a model to explore the semantic context in text sequences based on the Named Entity Recognition (NER) method in the NLP field. In this paper, we propose to harness the effective information from both semantic meaning and spatial distribution of texts in documents. Specifically, our proposed model, Convolutional Universal Text Information Extractor (CUTIE), applies convolutional neural networks on gridded texts where texts are embedded as features with semantical connotations. We further explore the effect of employing different structures of convolutional neural network and propose a fast and portable structure. We demonstrate the effectiveness of the proposed method on a dataset with up to $4,484$ labelled receipts, without any pre-training or post-processing, achieving state of the art performance that is much higher than the BERT for NER but with only $1/10$ parameters and without requiring the $3,300$M word dataset for pre-training. Experimental results also demonstrate that the proposed CUTIE model being able to achieve the state of the art performance in terms of either speed and accuracy with a much smaller amount of training data.
\end{abstract}

@@

\begin{table*}
	\caption{Performance comparison on different types of documents. (AP/softAP)}
\begin{center}
\begin{tabular}{l | c | c | c | c}
	Method & \#Params & Taxi & ME & Hotel \\
	\hline
	CloudScan\cite{cloudscan} & - & 82 / - & 64 / - & 60 / - \\
	BERT\cite{bert} & 110M & 88.1 / - & 80.1 / - & 71.7 / - \\
	CUTIE-A & 67M & 90.8 / 97.2 & 77.7 / \textbf{91.4} & 69.5 / \textbf{87.8} \\
	CUTIE-B & 14M & \textbf{94.0} / \textbf{97.3} & \textbf{81.5} / 89.7 & \textbf{74.6} / 87.0 \\
	%CUTIE-A split & 67M & 92.9 / 96.7 & 81.4 / 91.6 & 72.3 / 95.0 \\
	%CUTIE-B split & 14M & 95.2 / 97.6 & 84.3 / 92.4 & 70.8 / 89.4 \\
\end{tabular}
\end{center}
	\label{tab:comparison}
\end{table*}

@@

We compare the performance of the proposed method with two state of the art methods CloudScan \cite{cloudscan} and BERT \cite{bert}. For comparison, the Cloud Scan model for SROIE is trained from scratch but with several expert designed features as described in \cite{cloudscan}. The BERT model for SROIE is transform learned with the Google released base model that is pre-trained on a huge dataset with $3,300$M words \cite{bert,bertgit}. To provide a fair comparison, $4,484$ samples with around $1,500$ each from Taxi, Meals Entertainment (ME), and Hotel, where $3,375$ samples are used for training and $1,125$ are used for testing, as reported in Table \ref{tab:dataset}. A single model is trained on the dataset for all these $3$ types of document receipts either for CloudScan, BERT, or CUTIE.

@@

\subsection{Overall Performance}
We report results of our method in terms of AP and compare with other state of the art methods in Table \ref{tab:comparison}. We also provide softAP results for CUTIE-A and CUTIE-B in Table \ref{tab:comparison}, where both the softAP of CUTIE-A and CUTIE-B exceeds their AP by a large margin.  Examples of inference results are illustrated in Figure \ref{fig:result}. Our big network CUTIE-A achieves $90.8\%$ AP and $97.2\%$ softAP on taxi receipts, $77.7\%$ AP and $91.4\%$ softAP on meals entertainment receipts, and $69.5\%$ AP and $87.8\%$ softAP on hotel receipts. Compared to CloudScan, CUTIE-A and CUTIE-B outperforms in every single test case. Furthermore, compared to BERT, which is pre-trained on a dataset with $3,300$M words and transfer learned on our dataset, our big network CUTIE-A improves AP by $2.7\%$ AP on taxi receipts but less accurate on other type of documents while using only $1/2$ parameters; our small network CUTIE-B improves AP by $5.9\%$ on taxi receipts, $1.4\%$ points on meals entertainment receipts, and $2.9\%$ on hotel receipts, outperforming other methods in all of the test cases but with much less complexity and smaller model size with only $1/9$ parameters and without requiring a huge dataset for model pretraining. We will further prove in Section \ref{parameters} that CUTIE-B is also able to achieve state of the art performance with only $1/10$ of BERT's parameters. Although CUTIE-B is smaller in capacity, it outperforms CUTIE-A in several assessment criterias. This is because CUTIE-B enlarges the field of view by employing the atrous convolution rather than the pooling or striding processes, the CUTIE-B model has a larger field of view and better understanding of tokens' relative spatial relationship since no restriction is applied on the feature maps shapes.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
   Extracting key information from documents, such as receipts or invoices, and preserving the interested texts to structured data is crucial in the document-intensive streamline processes of office automation in areas that includes but not limited to accounting, financial, and taxation areas. To avoid designing expert rules for each specific type of document, some published works attempt to tackle the problem by learning a model to explore the semantic context in text sequences based on the Named Entity Recognition (NER) method in the NLP field. In this paper, we propose to harness the effective information from both semantic meaning and spatial distribution of texts in documents. Specifically, our proposed model, Convolutional Universal Text Information Extractor (CUTIE), applies convolutional neural networks on gridded texts where texts are embedded as features with semantical connotations. We further explore the effect of employing different structures of convolutional neural network and propose a fast and portable structure. We demonstrate the effectiveness of the proposed method on a dataset with up to $4,484$ labelled receipts, without any pre-training or post-processing, achieving state of the art performance that is much better than the NER based methods in terms of either speed and accuracy. Experimental results also demonstrate that the proposed CUTIE model being able to achieve good performance with a much smaller amount of training data.
\end{abstract}

@@

\begin{table*}
	\caption{Performance comparison on different types of documents. (AP/softAP)}
\begin{center}
\begin{tabular}{l | c | c | c | c}
	Method & \#Params & Taxi & ME & Hotel \\
	\hline
	CloudScan\cite{cloudscan} & - & 82 / - & 64 / - & 60 / - \\
	BERT for NER\cite{bert} & 110M & 88.1 / - & 80.1 / - & 71.7 / - \\
	CUTIE-A & 67M & 90.8 / 97.2 & 77.7 / \textbf{91.4} & 69.5 / \textbf{87.8} \\
	CUTIE-B & 14M & \textbf{94.0} / \textbf{97.3} & \textbf{81.5} / 89.7 & \textbf{74.6} / 87.0 \\
	%CUTIE-A split & 67M & 92.9 / 96.7 & 81.4 / 91.6 & 72.3 / 95.0 \\
	%CUTIE-B split & 14M & 95.2 / 97.6 & 84.3 / 92.4 & 70.8 / 89.4 \\
\end{tabular}
\end{center}
	\label{tab:comparison}
\end{table*}

@@

We compare the performance of the proposed method with two state of the art methods CloudScan \cite{cloudscan} and BERT for NER \cite{bert}. For comparison, the Cloud Scan model for SROIE is trained from scratch but with several expert designed features as described in \cite{cloudscan}. The BERT model for SROIE is transform learned with the Google released base model that is pre-trained on a huge dataset with $3,300$M words \cite{bert,bertgit}. To provide a fair comparison, $4,484$ samples with around $1,500$ each from Taxi, Meals Entertainment (ME), and Hotel, where $3,375$ samples are used for training and $1,125$ are used for testing, as reported in Table \ref{tab:dataset}. A single model is trained on the dataset for all these $3$ types of document receipts either for CloudScan, BERT, or CUTIE.

@@

\subsection{Overall Performance}
We report results of our method in terms of AP and compare with other state of the art methods in Table \ref{tab:comparison}. We also provide softAP results for CUTIE-A and CUTIE-B in Table \ref{tab:comparison}, where both the softAP of CUTIE-A and CUTIE-B exceeds their AP by a large margin.  Examples of inference results are illustrated in Figure \ref{fig:result}. Our big network CUTIE-A achieves $90.8\%$ AP and $97.2\%$ softAP on taxi receipts, $77.7\%$ AP and $91.4\%$ softAP on meals entertainment receipts, and $69.5\%$ AP and $87.8\%$ softAP on hotel receipts. Compared to CloudScan, CUTIE-A and CUTIE-B outperforms in every single test case. Furthermore, compared to BERT for NER, which is pre-trained on a dataset with $3,300$M words and transfer learned on our dataset, our big network CUTIE-A improves AP by $2.7\%$ AP on taxi receipts but less accurate on other type of documents while using only $1/2$ parameters; our small network CUTIE-B improves AP by $5.9\%$ on taxi receipts, $1.4\%$ points on meals entertainment receipts, and $2.9\%$ on hotel receipts, outperforming other methods in all of the test cases but with much less complexity and smaller model size with only $1/9$ parameters and without requiring a huge dataset for model pretraining. We will further prove in Section \ref{parameters} that CUTIE-B is also able to achieve state of the art performance with only $1/10$ of BERT's parameters. Although CUTIE-B is smaller in capacity, it outperforms CUTIE-A in several assessment criterias. This is because CUTIE-B enlarges the field of view by employing the atrous convolution rather than the pooling or striding processes, the CUTIE-B model has a larger field of view and better understanding of tokens' relative spatial relationship since no restriction is applied on the feature maps shapes.
